---
title: "P25322_WB LLRP I Field Activity"
subtitle: "MSE Baseline · C4ED"
logo: logo.png
format:
  dashboard:
    theme: flatly
    nav-buttons: 
      - icon: gitlab
        href: "https://github.com/yebelay"
    orientation: rows
    scrolling: true
    embed-resources: false
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
source("R/process_data.R")
```

```{r helpers}
#| include: false
library(htmltools)
library(glue)
library(plotly)
library(dplyr)
library(bslib)

pal <- list(
  navy  = "#004D40",
  blue  = "#00796B",
  green = "#00695C",
  amber = "#26A69A",
  red   = "#4DB6AC",
  gray  = "#E0F2F1",
  t6    = c("#004D40","#00695C","#00897B","#26A69A","#80CBC4","#B2DFDB"),
  arms  = c(Control="#B2DFDB", `Human-led Training`="#00897B",
            `Tech-based Training`="#004D40"))

pl_layout <- function(p, ...) {
  layout(p,
    font          = list(family = "Segoe UI, Arial", size = 11, color = "#595959"),
    paper_bgcolor = "rgba(0,0,0,0)",
    plot_bgcolor  = "rgba(0,0,0,0)",
    margin        = list(l = 40, r = 10, t = 30, b = 40),
    legend        = list(orientation = "h", y = 1.12, x = 0,
                         font = list(size = 10), bgcolor = "rgba(0,0,0,0)"),
    ...
  )
}

data_tag <- tags$script(HTML(paste0("const D=", D_js, ";")))

helpers_js <- tags$script(HTML('
const C={
  navy:"#004D40",blue:"#00796B",green:"#00695C",amber:"#26A69A",
  red:"#4DB6AC",gray:"#E0F2F1",
  t6:["#004D40","#00695C","#00897B","#26A69A","#80CBC4","#B2DFDB"],
  tc:{Daniel:"#009688",Anteneh:"#00796B",Wesen:"#4DB6AC",Muktar:"#80CBC4"},
  arms:{"Control":"#B2DFDB","Human-led Training":"#00897B",
        "Tech-based Training":"#004D40"}
};
function pc(p){return p>=100?C.green:p>=60?C.blue:p>=30?C.amber:C.red}
function pill(s){
  if(s==="Complete")    return\'<span class="pill pc">✅ Complete</span>\';
  if(s==="In Progress") return\'<span class="pill pip">🔄 In Progress</span>\';
  return\'<span class="pill pn">⏳ Not Started</span>\';
}
const lbs=D.daily.map(d=>d.date);
const mRP=D.daily.map(d=>d.mse_pace);
const sRP=D.daily.map(d=>d.sp_pace);
'))

kpi_card <- function(label, value, sub, bar_pct = NULL, color_class = "") {
  bar_html <- if (!is.null(bar_pct)) {
    glue('<div class="kb"><div class="kf {color_class}" style="width:{min(bar_pct,100)}%"></div></div>')
  } else ""
  HTML(glue('
    <div class="kpi {color_class}">
      <div class="kl">{label}</div>
      <div class="kv">{value}</div>
      <div class="ks">{sub}</div>
      {bar_html}
    </div>
  '))
}
```

```{r css}
#| output: asis
cat('<style>
:root{
  --navy:#0C6D71;--teal:#00796B;--dk-teal:#004D40;
  --blue:#E0F2F1;--lb:#B2DFDB;--vlb:#E0F2F1;
  --green:#00695C;--lg:#E0F2F1;--gt:#004D40;
  --amber:#26A69A;--la:#B2DFDB;--at:#00695C;
  --red:#4DB6AC;--lr:#E0F2F1;--gray:#F2F2F2;
  --dg:#595959;--border:#B2DFDB;--white:#fff;
  --font:\'Segoe UI\',Arial,sans-serif
}
*{box-sizing:border-box}
body{font-family:var(--font);font-size:18px}

/* ── Navbar ── */
.navbar,
.navbar-default,
.quarto-dashboard .navbar {
  background-color:#0C6D71 !important;
  border-bottom:none !important;
}
.navbar .navbar-brand,
.navbar .navbar-brand *,
.navbar-title,
.navbar-subtitle,
.quarto-dashboard-title,
.quarto-dashboard-subtitle { color:#ffffff !important; opacity:1 !important; }
.navbar .nav-link,
.navbar .nav-item a,
.navbar .navbar-nav .nav-link,
.navbar-default .navbar-nav > li > a,
.quarto-dashboard .navbar .nav-link { color:#ffffff !important; opacity:1 !important; }
.navbar .nav-link.active,
.navbar .nav-item.active > a {
  background-color:rgba(255,255,255,0.18) !important;
  color:#ffffff !important;
  border-radius:6px;
}
.navbar .nav-link:hover {
  background-color:rgba(255,255,255,0.10) !important;
  color:#ffffff !important;
}
.navbar .bi,
.navbar svg { color:#ffffff !important; fill:#ffffff !important; }
.navbar .nav-button,
.navbar .btn,
.navbar .quarto-nav-button { color:#ffffff !important; }

/* Force title + subtitle to stack */
.navbar-brand {
  display: flex !important;
  flex-direction: column !important;
  align-items: flex-start !important;
}

/* Target ALL possible title/subtitle classes */
.navbar-title,
.quarto-dashboard-title {
  display: block !important;
  font-weight: 700;
  line-height: 1.2;
}

.navbar-subtitle,
.quarto-dashboard-subtitle {
  display: block !important;
  font-size: 11px;
  margin-top: 2px;
  opacity: 0.85;
}

/* ── bslib value_box base ── */
/* Longhands only — never shorthand border-left — so inline style= can override color */
.bslib-value-box {
  background:        #fff !important;
  border:            none !important;
  border-left-width: 4px !important;
  border-left-style: solid !important;
  border-left-color: #B2DFDB !important;
  border-radius:     8px !important;
  box-shadow:        0 1px 3px rgba(0,0,0,.07) !important;
  min-height:        unset !important;
  padding:           0 !important;
  position:          relative !important;
  overflow:          hidden !important;
}
.bslib-value-box .value-box-grid {
  display:        flex !important;
  flex-direction: column !important;
  padding:        10px 13px 16px !important;
  gap:            2px !important;
}
.bslib-value-box .value-box-showcase { display:none !important; }
.bslib-value-box .value-box-area     { padding:0 !important; }
.bslib-value-box .value-box-title {
  font-size:      9px !important;
  color:          var(--dg) !important;
  text-transform: uppercase !important;
  letter-spacing: .5px !important;
  font-weight:    600 !important;
  margin:         0 !important;
  opacity:        1 !important;
}
.bslib-value-box .value-box-value {
  font-size:   24px !important;
  font-weight: 700 !important;
  color:       var(--navy) !important;
  line-height: 1.1 !important;
  margin:      0 !important;
}
.bslib-value-box p {
  font-size:   9px !important;
  color:       var(--dg) !important;
  font-weight: 400 !important;
  margin:      0 !important;
}

/* ── Progress bar at bottom via ::after ──
   Reads --vb-bar-color and --vb-pct from inline style= on the element.
   Variant classes set sensible defaults; inline style= overrides freely.      */
.bslib-value-box::after {
  content:       "";
  position:      absolute;
  bottom:        10px;
  left:          4px;
  height:        6px;
  width:         100%;
  border-radius: 0 0 8px 8px;
  background: linear-gradient(
    to right,
    var(--vb-bar-color, #B2DFDB) var(--vb-pct, 0%),
    #E0F2F1                      var(--vb-pct, 0%)
  );
}

/* ── Per-variant defaults ──
   border-left-color  : accent colour for the left stripe
   --vb-bar-color     : default bar colour (can be overridden per-box via style=)
   Inline style= on the value_box() call wins over all of these.               */
.bslib-value-box.vb-green {
  border-left-color: #00695C !important;
  --vb-bar-color:    #00695C;
}
.bslib-value-box.vb-amber {
  border-left-color: #ff8d00 !important;
  --vb-bar-color:    #26A69A;
}
.bslib-value-box.vb-red {
  border-left-color: #4DB6AC !important;
  --vb-bar-color:    #4DB6AC;
}

/* ── KPI cards (custom HTML) ── */
.kr{display:flex;flex-wrap:wrap;gap:10px;margin-bottom:14px}
.kpi{background:#fff;border-radius:8px;padding:12px 14px;
     border-left:4px solid var(--lb);box-shadow:0 1px 3px rgba(0,0,0,.07);
     min-width:130px;flex:1}
.kpi.g{border-left-color:var(--green)}
.kpi.a{border-left-color:var(--amber)}
.kpi.r{border-left-color:var(--red)}
.kl{font-size:9px;color:var(--dg);text-transform:uppercase;letter-spacing:.5px;margin-bottom:3px}
.kv{font-size:24px;font-weight:700;color:var(--navy);line-height:1.1}
.ks{font-size:9px;color:var(--dg);margin-top:3px}
.kb{height:4px;background:var(--border);border-radius:2px;margin-top:7px}
.kf{height:100%;border-radius:2px;transition:width .8s}
.kf.b{background:var(--teal)}.kf.g{background:var(--green)}
.kf.a{background:var(--amber)}.kf.r{background:var(--red)}

/* ── Alert banners ── */
.alert{padding:9px 14px;border-radius:6px;font-size:11px;margin-bottom:12px}
.aw{background:#FFF9E6;border:1px solid var(--la);color:var(--at)}
.ad{background:var(--lr);border:1px solid var(--red);color:var(--red)}
.ag{background:var(--lg);border:1px solid #A9D18E;color:var(--gt)}
.alert strong{font-weight:700}

/* ── Section headers ── */
.sec{font-size:11px;font-weight:700;color:var(--navy);text-transform:uppercase;
     letter-spacing:.5px;padding-left:8px;border-left:3px solid var(--teal);
     margin:16px 0 10px}

/* ── Chart containers ── */
.cg{display:grid;grid-template-columns:repeat(auto-fit,minmax(300px,1fr));gap:12px;margin-bottom:12px}
.cg3{display:grid;grid-template-columns:repeat(auto-fit,minmax(220px,1fr));gap:12px;margin-bottom:12px}
.cw{display:grid;grid-template-columns:1fr;gap:12px;margin-bottom:12px}
.cc{background:#fff;border-radius:8px;padding:13px 15px;box-shadow:0 1px 3px rgba(0,0,0,.07)}
.cc h3{font-size:10px;font-weight:700;color:var(--navy);text-transform:uppercase;
        letter-spacing:.4px;margin-bottom:8px}
.ch{position:relative}

/* ── Tables ── */
.tc{background:#fff;border-radius:8px;padding:13px 15px;
    box-shadow:0 1px 3px rgba(0,0,0,.07);margin-bottom:12px;overflow-x:auto}
.tc h3{font-size:10px;font-weight:700;color:var(--navy);text-transform:uppercase;
       letter-spacing:.4px;margin-bottom:8px}
table{width:100%;border-collapse:collapse;font-size:11px}
th{background:var(--navy);color:#fff;padding:6px 9px;text-align:left;
   font-weight:600;font-size:9px;text-transform:uppercase;letter-spacing:.3px}
td{padding:5px 9px;border-bottom:1px solid var(--border)}
tr:nth-child(even) td{background:#F8FAFC}
tr:hover td{background:var(--vlb)}
.pill{display:inline-block;padding:2px 8px;border-radius:10px;font-size:9px;font-weight:700}
.pc{background:var(--lg);color:var(--gt)}
.pip{background:var(--la);color:var(--at)}
.pn{background:var(--gray);color:var(--dg)}
.pr{background:var(--lr);color:var(--red)}
.mb{display:flex;align-items:center;gap:5px}
.mbt{flex:1;height:5px;background:var(--border);border-radius:3px;min-width:50px}
.mbf{height:100%;border-radius:3px}
.mv{font-weight:700;font-size:10px;min-width:32px}
tr.fur td{background:#FFF0F0!important}
tr.fur:hover td{background:var(--lr)!important}
.mb2{background:var(--red);color:#fff;font-size:9px;font-weight:700;
     padding:1px 6px;border-radius:8px}

/* ── Quarto card padding ── */
.card-body{padding:8px 10px !important}
.card-header{padding:6px 10px !important;font-size:10px !important}
</style>')
```

```{r inject_data}
#| output: asis
cat(as.character(tagList(data_tag, helpers_js)))
```

# Overview

## Note {height="auto"}

```{r ov_alert}
#| output: asis
HTML(glue('
<div class="alert" style="background:#FFF8E1;border:1px solid #FFD54F;color:#3E2723;font-size:12px;">
  <strong>⚠️{k$data_date} Status: {k$mse_i} MSE members ({k$mse_u} MSEs) interviewed·
  🔴 {k$mse_incomp} MSEs need follow-up (missing respondents)·
  {k$sp_i} spouse interviews·
  🔴 {k$sp_incomp} MSEs need 2nd spouse -
  <span style="color:#E65100;text-decoration:underline;">see Follow-up Alerts tab</span></strong>
</div>'))
```

## Value boxes {height="100px"}

```{r vb_mse_i}
# --vb-bar-color controls the bottom bar independently of border-left-color
# Pass different hex values to have them differ, or the same to match.
mse_pct_num <- as.numeric(k$mse_pct)
value_box(
  title    = "Total Interviewed Respondents",
  value    = k$mse_i,
  showcase = NULL,
  p(paste0("of 2,160 target (", k$mse_pct, "%)")),
  class    = "vb-green",
  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#13D4D4; --vb-pct:{mse_pct_num}%;"))
```

```{r vb_mse_comp}
mse_comp_pct <- round(as.numeric(k$mse_comp) / 360 * 100)
value_box(
  title    = "MSEs Complete 6/6",
  value    = k$mse_comp,
  showcase = NULL,
  p("of 360 MSE target"),
  class    = "vb-red",
  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#13D4D4; --vb-pct:{mse_comp_pct}%;")
)
```


```{r vb_mse_incomp}
#| content: valuebox
#| title: "MSEs Incomplete"
list(value=k$mse_incomp, 
     caption="need follow-up upload", 
     color = "white",
     icon=NULL,
     style    = glue("border-left-color:#4DB6AC !important"))
```

```{r vb_sp_i}
sp_pct_num <- as.numeric(k$sp_pct)
value_box(
  title    = "Total Spouses interviewed",
  value    = k$sp_i, 
  showcase = NULL,
  p(paste0("of 480 target (", k$sp_pct, "%)")),
  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#13D4D4; --vb-pct:{sp_pct_num}%;"))
```

```{r vb_sp_comp}
#| content: valuebox
#| title: "Spouse 2/2 Complete"
list(value=k$sp_comp, caption="MSEs with both spouses", 
     color="#20c997", 
     icon=NULL)
```

```{r vb_sp_incomp}
#| content: valuebox
#| title: "Spouse Incomplete"
list(value=k$sp_incomp, caption="only 1/2 submitted", 
     color = "white", icon=NULL)
```

```{r vb_woredas}
#| content: valuebox
#| title: "Woredas Active"
list(value=k$woredas_active, caption="of 36 total", color="white", icon=NULL)
```

```{r vb_days}
#| content: valuebox
#| title: "Field Days"
list(value=k$n_days, caption=paste0(k$date_start," – ",k$date_end), 
     color= "white", icon=NULL)
```


## Row {height="300px"}

```{r ov_chart2}
#| title: "📊 Daily MSE & Spouse Interviews"
plot_ly(daily, x = ~date) |>
  add_bars(y = ~mse_i, name = "MSE",    marker = list(color = pal$blue,  line = list(width = 0))) |>
  add_bars(y = ~sp_i,  name = "Spouse", marker = list(color = pal$amber, line = list(width = 0))) |>
  pl_layout(barmode = "group", yaxis = list(rangemode = "tozero", title = ""),
xaxis = list(
      tickangle = -45,
      dtick = "D1",
      tickformat = "%b %d",
      tickfont = list(size = 10))) |>
  config(displayModeBar = FALSE)
```

```{r ov_chart3}
#| title: "✅ MSE Completion Status (360 total)"
mse_complete   <- k$mse_comp
mse_incomplete <- nrow(fu_mse_tbl)
mse_notstarted <- max(360 - mse_complete - mse_incomplete, 0)
plot_ly(
  labels = c(paste0("Complete 6/6 (", mse_complete, ")"),
             paste0("Underway (", mse_incomplete, ")"),
             "Not Started"),
  values = c(mse_complete, mse_incomplete, mse_notstarted),
  type   = "pie", hole = 0.55,
  marker = list(colors = c(pal$green, pal$amber, pal$gray),
                line = list(color = "#fff", width = 2)),
  textinfo = "label+percent"
) |>
  pl_layout(showlegend = TRUE, legend = list(orientation = "v", x = 1, y = 0.5)) |>
  config(displayModeBar = FALSE)
```

## Row {height="250px"}

```{r ov_chart4}
#| title: "👥 Interviews by Team"
# team6_sum is already in environment from process_data.R
team6 <- team6_sum
plot_ly(team6, x = ~team, y = ~i, type = "bar",
        marker = list(color = pal$t6, line = list(width = 0)),
        name = "Interviews") |>
  pl_layout(showlegend = FALSE, yaxis = list(rangemode = "tozero", title = "")) |>
  config(displayModeBar = FALSE)
```

```{r ov_chart5}
#| title: "🔬 Treatment Arm Balance"
# arm_sum is already in environment from process_data.R
arm <- arm_sum
arm_colors <- ifelse(arm$a %in% names(pal$arms), pal$arms[arm$a], pal$gray)
plot_ly(
  labels = arm$a, values = arm$i, type = "pie", hole = 0.55,
  marker = list(colors = arm_colors, line = list(color = "#fff", width = 2)),
  textinfo = "label+percent"
) |>
  pl_layout(showlegend = TRUE, legend = list(orientation = "v", x = 1, y = 0.5)) |>
  config(displayModeBar = FALSE)
```

```{r ov_chart6}
#| title: "Spouse Status (240 treatment MSEs)"
sp_comp_ov    <- sum(team6$sp_comp, na.rm = TRUE)
sp_incomp_ov  <- nrow(fu_sp_tbl)
sp_started_ov <- sum(team6$sm, na.rm = TRUE)
plot_ly(
  labels = c(paste0("2/2 Complete (", sp_comp_ov, ")"),
             paste0("1/2 Only (", sp_incomp_ov, ")"),
             "Not yet"),
  values = c(sp_comp_ov, sp_incomp_ov, max(240 - sp_started_ov, 0)),
  type = "pie", hole = 0.55,
  marker = list(colors = c(pal$green, pal$amber, pal$gray),
                line = list(color = "#fff", width = 2)),
  textinfo = "label+percent"
) |>
  pl_layout(showlegend = TRUE, legend = list(orientation = "v", x = 1, y = 0.5)) |>
  config(displayModeBar = FALSE)
```

# 🔔 Follow-up 

## Row {height="auto"}

```{r fu_alert}
#| output: asis
HTML(glue('
<div class="alert" style="background:#FFF8E1;border:1px solid #FFD54F;color:#3E2723;font-size:12px;">
  <strong>🔔 ACTION REQUIRED:</strong>
  {k$mse_incomp} MSEs have fewer than 6 interviews uploaded.
  {k$sp_incomp} MSEs have only 1 spouse interview.
  Notify the relevant supervisor to upload missing data from SurveyCTO.
</div>
'))
```

## Row

```{r fu_chart1}
#| title: "⚠️ Follow-up by Team (MSE)"
plot_ly(team6, x = ~team, y = ~fu_mse, type = "bar",
        marker = list(color = pal$t6, line = list(width = 0)),
        name = "MSEs needing follow-up") |>
  pl_layout(showlegend = FALSE, yaxis = list(rangemode = "tozero", dtick = 1, title = "")) |>
  config(displayModeBar = FALSE)
```

```{r fu_chart2}
#| title: "⚠️ Follow-up by Team (Spouse)"
plot_ly(team6, x = ~team, y = ~fu_sp, type = "bar",
        marker = list(color = pal$t6, line = list(width = 0)),
        name = "Spouse follow-up needed") |>
  pl_layout(showlegend = FALSE, yaxis = list(rangemode = "tozero", dtick = 1, title = "")) |>
  config(displayModeBar = FALSE)
```

## Row {height="auto"}

```{r fu_table_mse}
#| output: asis
HTML(paste0('
<div class="sec">⚠️ MSE Follow-up -', k$mse_incomp, ' MSEs Missing Respondents</div>
<div class="tc">
  <h3>Notify supervisor to upload remaining interviews from SurveyCTO</h3>
  <table><thead><tr>
    <th>MSE ID</th><th>Woreda</th><th>Zone</th><th>Team</th><th>Supervisor</th>
    <th>Treatment Arm</th><th>Submitted</th><th>Missing</th><th>Last Upload</th><th>Action</th>
  </tr></thead><tbody id="tFuM"></tbody></table>
</div>
<div class="sec">Spouse Follow-up - ', k$sp_incomp, ' MSEs Missing 2nd Spouse</div>
<div class="tc">
  <h3>2nd spouse interview not yet uploaded</h3>
  <table><thead><tr>
    <th>MSE ID</th><th>Woreda</th><th>Team</th><th>Supervisor</th>
    <th>Treatment Arm</th><th>Submitted</th><th>Missing</th><th>Last Upload</th><th>Action</th>
  </tr></thead><tbody id="tFuS"></tbody></table>
</div>
<script>
document.getElementById("tFuM").innerHTML=D.fu_mse.map(r=>
  `<tr class="fur"><td><strong>${r.id}</strong></td><td>${r.w}</td><td>${r.z}</td>
  <td>${r.team}</td><td><strong>${r.sup}</strong></td><td>${r.arm}</td>
  <td>${r.i}/6</td><td><span class="mb2">Need ${r.miss}</span></td>
  <td>${r.dl}</td><td>📢 Notify ${r.sup}</td></tr>`).join("");
document.getElementById("tFuS").innerHTML=D.fu_sp.map(r=>
  `<tr class="fur"><td><strong>${r.id}</strong></td><td>${r.w}</td>
  <td>${r.team}</td><td><strong>${r.sup}</strong></td><td>${r.arm}</td>
  <td>${r.i}/2</td><td><span class="mb2">Need ${r.miss}</span></td>
  <td>${r.dl}</td><td>📢 Notify ${r.sup}</td></tr>`).join("");
</script>
'))
```

# Daily Progress

## Row

```{r dy_chart_pace}
#| title: "📈 Cumulative Progress vs Required Pace (2,160 MSE + 480 Spouse targets)"
plot_ly(daily, x = ~date) |>
  add_trace(y = ~cum_mse,  name = "MSE Actual", type = "scatter", mode = "lines+markers",
            line = list(color = pal$blue,  width = 2.5),
            marker = list(size = 6, color = pal$blue),
            fill = "tozeroy", fillcolor = "rgba(0,121,107,.12)") |>
  add_trace(y = ~mse_pace, name = "MSE Pace",       type = "scatter", mode = "lines",
            line = list(color = pal$blue, dash = "dash", width = 1.5),
            marker = list(size = 0)) |>
  add_trace(y = ~cum_sp,   name = "Spouse Actual",  type = "scatter", mode = "lines+markers",
            line = list(color = pal$amber, width = 2),
            marker = list(size = 6, color = pal$amber),
            fill = "tozeroy", fillcolor = "rgba(38,166,154,.10)") |>
  add_trace(y = ~sp_pace,  name = "Spouse Pace",    type = "scatter", mode = "lines",
            line = list(color = pal$amber, dash = "dash", width = 1.5),
            marker = list(size = 0)) |>
  pl_layout(yaxis = list(rangemode = "tozero", title = ""),
            xaxis = list(
      tickangle = -45,
      dtick = "D1",
      tickformat = "%b %d",
      tickfont = list(size = 10)  ),

    legend = list(
      orientation = "h",  x = 0, y = 1.15    )) |>
  config(displayModeBar = TRUE)
```


## Row

```{r dy_chart_mse}
#| title: "MSE Interviews per Day"
plot_ly(daily, x = ~date, y = ~mse_i, type = "bar",
        marker = list(color = pal$blue, line = list(width = 0))) |>
  pl_layout(showlegend = FALSE, yaxis = list(rangemode = "tozero", title = ""), 
            xaxis = list(
      tickangle = -45,
      dtick = "D1",
      tickformat = "%b %d",
      tickfont = list(size = 10)  )) |>
  config(displayModeBar = FALSE)
```

```{r dy_chart_sp}
#| title: "Spouse Interviews per Day"
plot_ly(daily, x = ~date, y = ~sp_i, type = "bar",
        marker = list(color = pal$amber, line = list(width = 0))) |>
  pl_layout(showlegend = FALSE, yaxis = list(rangemode = "tozero", title = ""),
            xaxis = list(
      tickangle = -45,
      dtick = "D1",
      tickformat = "%b %d",
      tickfont = list(size = 10)  )) |>
  config(displayModeBar = FALSE)
```

## Row {height="auto"}

```{r dy_table}
#| output: asis
HTML('
<div class="tc"><h3>Day-by-Day Summary</h3>
<table><thead><tr>
  <th>Date</th><th>MSE memberes Interviewed</th><th>Spouse Interviewed</th><th>Cum. MSE</th><th>Cum. Spouse</th><th>% MSE Target</th>
</tr></thead><tbody id="tDay"></tbody></table></div>
<script>
document.getElementById("tDay").innerHTML=D.daily.map(d=>`
  <tr><td><strong>${d.date}</strong></td><td>${d.mse_i}</td>
  <td>${d.sp_i}</td><td><strong>${d.cum_mse}</strong></td><td><strong>${d.cum_sp}</strong></td>
  <td><div class="mb"><div class="mbt"><div class="mbf" style="width:${Math.min(d.cum_mse/2160*100,100).toFixed(1)}%;background:${pc(d.cum_mse/2160*100)}"></div></div>
  <span class="mv">${(d.cum_mse/2160*100).toFixed(1)}%</span></div></td></tr>`).join("");
</script>
')
```

# Teams

## Row

```{r tm_chart1}
#| title: "MSE Interviews by Team"
plot_ly(team6, x = ~team) |>
  add_bars(y = ~comp,  name = "Complete 6/6",
           marker = list(color = "#00695C", line = list(width = 0))) |>
  add_bars(y = ~incomp, name = "Incomplete",
           marker = list(color = "#26A69A", line = list(width = 0))) |>
  pl_layout(barmode = "stack", yaxis = list(rangemode = "tozero", title = "")) |>
  config(displayModeBar = T)
```

```{r tm_chart2}
#| title: "Enumerator Interviews (Top 20)"
enums_top20 <- enum_sum |> arrange(desc(i)) |> head(20)
plot_ly(enums_top20,
        y = ~paste0(e, " (", sup, ")"), x = ~i,
        type = "bar", orientation = "h",
        marker = list(color = pal$blue, line = list(width = 0))) |>
  pl_layout(showlegend = FALSE,
            yaxis = list(categoryorder = "total ascending", title = ""),
            xaxis = list(rangemode = "tozero", title = "Interviews"),
            margin = list(l = 130, r = 10, t = 30, b = 40)) |>
  config(displayModeBar = FALSE)
```

## Row {height="auto"}

```{r tm_table1}
#| output: asis
HTML('
<div class="tc"><h3>Team Summary (by Individual Team A-F)</h3>
<table><thead><tr>
  <th>Team</th><th>MSE Interviews</th><th>MSEs Active</th><th>Complete 6/6</th>
  <th>Incomplete</th><th>Spouse Interviews</th><th>MSE Follow-up</th><th>Spouse Follow-up</th>
</tr></thead><tbody id="tTm"></tbody></table></div>
<div class="tc"><h3>Enumerator Detail</h3>
<table><thead><tr>
  <th>Supervisor</th><th>Enumerator</th><th>Interviews</th><th>MSEs</th><th>Avg/MSE</th>
</tr></thead><tbody id="tEn"></tbody></table></div>
<script>
document.getElementById("tTm").innerHTML=D.team6.map(t=>`
  <tr>
    <td><strong>${t.team}</strong></td>
    <td>${t.i}</td><td>${t.m}</td>
    <td><span style="color:#00695C;font-weight:700">${t.comp}</span></td>
    <td>${t.incomp>0?`<span class="mb2">${t.incomp}</span>`:"✅ 0"}</td>
    <td>${t.si||0}</td>
    <td>${t.fu_mse>0?`<span class="mb2">${t.fu_mse} MSEs</span>`:"✅ 0"}</td>
    <td>${t.fu_sp>0?`<span class="mb2">${t.fu_sp} MSEs</span>`:"✅ 0"}</td>
  </tr>`).join("");
document.getElementById("tEn").innerHTML=D.enums.map(e=>`
  <tr><td>${e.sup}</td><td><strong>${e.e}</strong></td><td>${e.i}</td><td>${e.m}</td>
  <td>${(e.i/e.m).toFixed(1)}</td></tr>`).join("");
</script>
')
```

# Treatment Arms

## Row {height="110px"}

```{r ar_vb_control}
#per_c <- as.numeric(arm_ctrl$p)
arm_ctrl <- arm_sum[arm_sum$a == "Control", ]
value_box(
  title    = "Control",
  value    = arm_ctrl$i,
  showcase = bsicons::bs_icon("circle"),
  p(paste0(arm_ctrl$m, " MSEs · ", arm_ctrl$p, "% of 720")),
  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#ff8d00; --vb-pct:{arm_ctrl$p}%;"))
```

```{r ar_vb_human}
#per_hm <- as.numeric(arm_hum$p)
arm_hum <- arm_sum[arm_sum$a == "Human-led Training", ]
value_box(
  title    = "Human-led Training",
  value    = arm_hum$i,
  showcase = bsicons::bs_icon("people-fill"),
  p(paste0(arm_hum$m, " MSEs · ", arm_hum$p, "% of 720")),
  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#ff8d00; --vb-pct:{arm_hum$p}%;"))
```

```{r ar_vb_tech}
#per_tc <- as.numeric(arm_tec$p)
arm_tec <- arm_sum[arm_sum$a == "Tech-based Training", ]
value_box(
  title    = "Tech-based Training",
  value    = arm_tec$i,
  showcase = bsicons::bs_icon("phone-fill"),
  p(paste0(arm_tec$m, " MSEs · ", arm_tec$p, "% of 720")),
  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#ff8d00; --vb-pct:{arm_tec$p}%;"))
```

## Row

```{r ar_chart1}
#| title: "Submitted vs Remaining per Arm"
plot_ly(arm, x = ~a) |>
  add_bars(y = ~i,
           name = "Submitted",
           marker = list(color = arm_colors, line = list(width = 0))) |>
  add_bars(y = ~pmax(t - i, 0),
           name = "Remaining",
           marker = list(color = "rgba(0,0,0,.07)", line = list(width = 0))) |>
  pl_layout(barmode = "stack",
            yaxis = list(rangemode = "tozero", range = c(0, 760), title = "")) |>
  config(displayModeBar = TRUE)
```

```{r ar_chart2}
#| title: "Progress per Arm (%)"
plot_ly(arm, x = ~a, y = ~p, type = "bar",
        marker = list(color = arm_colors, line = list(width = 0))) |>
  pl_layout(showlegend = FALSE,
            yaxis = list(rangemode = "tozero", range = c(0, 45), title = "%")) |>
  config(displayModeBar = FALSE)
```

# Woredas

## Row {height="100px"}
## Row {height="100px"}

```{r wr_vb_complete}
n_complete <- sum(woreda_cov$s == "Complete",    na.rm = TRUE)
value_box(
  title    = "Complete Woredas",
  value    = n_complete,
  showcase = bsicons::bs_icon("check-circle-fill"),
  p("100% interviews done"),
  theme = value_box_theme(bg = "#00695C", fg = "#ffffff"))
```

```{r wr_vb_progress}
n_progress <- sum(woreda_cov$s == "In Progress", na.rm = TRUE)
value_box(
  title    = "In Progress",
  value    = n_progress,
  showcase = bsicons::bs_icon("arrow-repeat"),
  p("partially surveyed"),
  theme    = value_box_theme(bg = "#26A69A", fg = "#ffffff")
)
```

```{r wr_vb_notstarted}
n_notstart <- sum(woreda_cov$s == "Not Started", na.rm = TRUE)
value_box(
  title    = "Not Started",
  value    = n_notstart,
  showcase = bsicons::bs_icon("hourglass"),
  p("yet to begin"),
  theme    = value_box_theme(bg = "#B2DFDB", fg = "#004D40")
)
```

```{r wr_vb_total}
value_box(
  title    = "Total Woredas",
  value    = nrow(woreda_cov),
  showcase = bsicons::bs_icon("map-fill"),
  p("across all zones"),
  theme    = value_box_theme(bg = "#004D40", fg = "#ffffff")
)
```

## Row

```{r wr_chart}
#| title: "🗺️ Woreda Status by Zone"
# woreda_cov is already in environment from process_data.R
woreda <- woreda_cov
zone_summary <- woreda |>
  group_by(z) |>
  summarise(
    Complete     = sum(s == "Complete"),
    `In Progress`= sum(s == "In Progress"),
    `Not Started` = sum(s == "Not Started"),
    .groups = "drop"
  ) |> arrange(z)

plot_ly(zone_summary, y = ~z) |>
  add_bars(x = ~Complete,      name = "Complete",     marker = list(color = pal$green)) |>
  add_bars(x = ~`In Progress`, name = "In Progress",  marker = list(color = pal$amber)) |>
  add_bars(x = ~`Not Started`, name = "Not Started",  marker = list(color = pal$gray))  |>
  pl_layout(barmode = "stack",
            yaxis = list(title = "", categoryorder = "category ascending"),
            xaxis = list(rangemode = "tozero", title = "Woredas"),
            margin = list(l = 90, r = 10, t = 30, b = 40)) |>
  config(displayModeBar = FALSE)
```

## Row {height="auto"}

```{r wr_table}
#| output: asis
HTML('
<div class="tc"><h3>Woreda-level Status</h3>
<table><thead><tr>
  <th>Zone</th><th>Woreda</th><th>Team</th><th>MSE Target</th><th>Int. Target</th>
  <th>Interviews</th><th>MSEs Active</th><th>Progress</th><th>Status</th>
</tr></thead><tbody id="tWor"></tbody></table></div>
<script>
document.getElementById("tWor").innerHTML=D.woreda.map(w=>`
  <tr><td>${w.z}</td><td><strong>${w.w}</strong></td><td>${w.t}</td>
  <td>${w.tgt}</td><td>${w.it}</td><td>${w.i}</td><td>${w.ms}</td>
  <td><div class="mb"><div class="mbt"><div class="mbf" style="width:${Math.min(w.p,100)}%;background:${pc(w.p)}"></div></div>
  <span class="mv">${w.p}%</span></div></td>
  <td>${pill(w.s)}</td></tr>`).join("");
</script>')
```

# Spousal 

## Row {height="120px"}

```{r sp_vb_sparm1}
a <- sp_by_sparm[1, ]
value_box(
  title    = paste0("Spousal: ", a$arm),
  value    = paste0(a$completed, " / ", a$eligible),
  showcase = bsicons::bs_icon("heart-fill"),
  p(paste0(a$pct, "% complete · ", a$started, " started · ", a$not_started, " not started")),  
  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#ff8d00; --vb-pct:{a$pct}%;"))
```

```{r sp_vb_sparm2}
a <- sp_by_sparm[2, ]
value_box(
  title    = paste0("Spousal: ", a$arm),
  value    = paste0(a$completed, " / ", a$eligible),
  showcase = bsicons::bs_icon("heart"),
  p(paste0(a$pct, "% complete · ", a$started, " started · ", a$not_started, " not started")),    style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#ff8d00; --vb-pct:{a$pct}%;"))
```

```{r sp_vb_edtarm1}
a <- sp_by_edtarm[1, ]
value_box(
  title    = paste0("Edutainment: ", a$arm),
  value    = paste0(a$completed, " / ", a$eligible),
  showcase = bsicons::bs_icon("film"),
  p(paste0(a$pct, "% complete · ", a$started, " started · ", a$not_started, " not started")), style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#ff8d00; --vb-pct:{a$pct}%;"))
```

```{r sp_vb_edtarm2}
a <- sp_by_edtarm[2, ]
value_box(
  title    = paste0("Edutainment: ", a$arm),
  value    = paste0(a$completed, " / ", a$eligible),
  showcase = bsicons::bs_icon("film"),
  p(paste0(a$pct, "% complete · ", a$started, " started · ", a$not_started, " not started")),  style    = glue("border-left-color:#0C6D71 !important; --vb-bar-color:#ff8d00; --vb-pct:{a$pct}%;"))
```


## Row

```{r sp_chart1}
#| title: "Spouse Interviews by Team"
plot_ly(team6, x = ~team) |>
  add_bars(y = ~sp_comp,  name = "Completed 2/2",
           marker = list(color = "#00695C", line = list(width = 0))) |>
  add_bars(y = ~sp_incomp, name = "Only 1/2",
           marker = list(color = "#26A69A", line = list(width = 0))) |>
  pl_layout(barmode = "stack", yaxis = list(rangemode = "tozero", title = ""), 
            xaxis = list(
      tickangle = -45,
      dtick = "D1",
      tickformat = "%b %d",
      tickfont = list(size = 10)  )) |>
  config(displayModeBar = TRUE)
```

```{r sp_chart2}
#| title: "Cumulative Spouse Interviews vs Pace"
plot_ly(daily, x = ~date) |>
  add_trace(y = ~cum_sp,  name = "Cumulative Spouse", type = "scatter", mode = "lines+markers",
            line = list(color = pal$amber, width = 2),
            marker = list(size = 5, color = pal$amber),
            fill = "tozeroy", fillcolor = "rgba(38,166,154,.10)") |>
  add_trace(y = ~sp_pace, name = "Required Pace",     type = "scatter", mode = "lines",
            line = list(color = pal$amber, dash = "dash", width = 1.5),
            marker = list(size = 0)) |>
  pl_layout(yaxis = list(rangemode = "tozero", title = "")) |>
  config(displayModeBar = FALSE)
```


## Row

```{r sp_chart3}
#| title: "By Spousal Support Assignment"
sp_sparm <- sp_by_sparm
plot_ly(sp_sparm, x = ~arm) |>
  add_bars(y = ~completed,  name = "Completed 2/2",
           marker = list(color = pal$green, line = list(width = 0))) |>
  add_bars(y = ~started,    name = "Started (1/2)",
           marker = list(color = pal$amber, line = list(width = 0))) |>
  add_bars(y = ~not_started, name = "Not Started",
           marker = list(color = pal$gray,  line = list(width = 0))) |>
  pl_layout(barmode = "stack", yaxis = list(rangemode = "tozero", title = "") ) |>
  config(displayModeBar = TRUE)
```

```{r sp_chart4}
#| title: "🎬 By Edutainment"
sp_edtarm <- sp_by_edtarm
plot_ly(sp_edtarm, x = ~arm) |>
  add_bars(y = ~completed,  name = "Completed 2/2",
           marker = list(color = pal$green, line = list(width = 0))) |>
  add_bars(y = ~started,    name = "Started (1/2)",
           marker = list(color = pal$amber, line = list(width = 0))) |>
  add_bars(y = ~not_started, name = "Not Started",
           marker = list(color = pal$gray,  line = list(width = 0))) |>
  pl_layout(barmode = "stack", yaxis = list(rangemode = "tozero", title = "")) |>
  config(displayModeBar = T)
```

## Row {height="auto"}

```{r sp_table}
#| output: asis
HTML(paste0('
<div class="tc"><h3>Spouse Follow-up Required (', k$sp_incomp, ' MSEs)</h3>
<table><thead><tr>
  <th>MSE ID</th><th>Woreda</th><th>Team</th><th>Supervisor</th>
  <th>Treatment Arm</th><th>Interviews</th><th>Status</th><th>Last Upload</th>
</tr></thead><tbody id="tSp"></tbody></table></div>
<script>
document.getElementById("tSp").innerHTML=D.fu_sp.map(r=>
  `<tr class="fur"><td><strong>${r.id}</strong></td><td>${r.w}</td>
  <td>${r.team}</td><td>${r.sup}</td><td>${r.arm}</td>
  <td>${r.i}/2</td><td><span class="pill pr">Need ${r.miss} more</span></td>
  <td>${r.dl}</td></tr>`).join("");
</script>
'))
```

# RCE 

## Row {height="60px"}

```{r rce_callout}
#| output: asis
# Info banner explaining the RCE design
n_flagged <- if (nrow(rce_enum) > 0) sum(rce_enum$flag_uniform, na.rm = TRUE) else 0
n_enum    <- if (nrow(rce_enum) > 0) n_distinct(rce_enum$enumerator) else 0
total_mis <- if (nrow(rce_enum) > 0) sum(rce_enum$mismatch, na.rm = TRUE) else 0
alert_cls <- if (n_flagged > 0) "alert-warning" else "alert-success"
alert_ico <- if (n_flagged > 0) "⚠️" else "✅"
HTML(glue('
<div class="alert {alert_cls}" role="alert" style="margin:4px 0;padding:8px 14px;font-size:13px;border-radius:6px">
  <strong>{alert_ico} Random Choice Experiment (RCE) Quality Check</strong> &nbsp;|&nbsp;
  4 blocks · 6 main choice questions (A/B/C) + 1 repeat consistency check each.
  &nbsp;<strong>{n_enum}</strong> enumerators &nbsp;·&nbsp;
  <strong>{total_mis}</strong> total answer mismatches &nbsp;·&nbsp;
  <strong style="color:#C62828">{n_flagged}</strong> enumerator-block(s) flagged (&ge;80% same letter).
</div>'))
```

## Row {height="115px"}

```{r rce_vb_b1}
#| padding: 4px
b <- rce_block[rce_block$block == 1, ]
if (nrow(b) == 0) b <- data.frame(block=1,n_resp=0,freq_A=0,freq_B=0,freq_C=0,pct_A=0,pct_B=0,pct_C=0,mismatches=0)
dom_col <- if (b$pct_A >= b$pct_B & b$pct_A >= b$pct_C) "#004D40" else
           if (b$pct_B >= b$pct_C) "#26A69A" else "#B2DFDB"
mis_txt <- if (b$mismatches > 0) paste0("⚠️ ", b$mismatches, " mismatch(es)") else "✅ 0 mismatches"
value_box(
  title    = "Block 1 · RCE",
  value    = paste0(b$n_resp, " responses"),
  showcase = bsicons::bs_icon("1-circle-fill"),
  p(paste0("A: ", b$pct_A, "% · B: ", b$pct_B, "% · C: ", b$pct_C, "%")),
  p(mis_txt),
  theme    = value_box_theme(bg = dom_col, fg = "#ffffff")
)
```

```{r rce_vb_b2}
#| padding: 4px
b <- rce_block[rce_block$block == 2, ]
if (nrow(b) == 0) b <- data.frame(block=2,n_resp=0,freq_A=0,freq_B=0,freq_C=0,pct_A=0,pct_B=0,pct_C=0,mismatches=0)
dom_col <- if (b$pct_A >= b$pct_B & b$pct_A >= b$pct_C) "#004D40" else
           if (b$pct_B >= b$pct_C) "#26A69A" else "#B2DFDB"
mis_txt <- if (b$mismatches > 0) paste0("⚠️ ", b$mismatches, " mismatch(es)") else "✅ 0 mismatches"
value_box(
  title    = "Block 2 · RCE",
  value    = paste0(b$n_resp, " responses"),
  showcase = bsicons::bs_icon("2-circle-fill"),
  p(paste0("A: ", b$pct_A, "% · B: ", b$pct_B, "% · C: ", b$pct_C, "%")),
  p(mis_txt),
  theme    = value_box_theme(bg = dom_col, fg = "#ffffff")
)
```

```{r rce_vb_b3}
#| padding: 4px
b <- rce_block[rce_block$block == 3, ]
if (nrow(b) == 0) b <- data.frame(block=3,n_resp=0,freq_A=0,freq_B=0,freq_C=0,pct_A=0,pct_B=0,pct_C=0,mismatches=0)
dom_col <- if (b$pct_A >= b$pct_B & b$pct_A >= b$pct_C) "#004D40" else
           if (b$pct_B >= b$pct_C) "#26A69A" else "#B2DFDB"
mis_txt <- if (b$mismatches > 0) paste0("⚠️ ", b$mismatches, " mismatch(es)") else "✅ 0 mismatches"
value_box(
  title    = "Block 3 · RCE",
  value    = paste0(b$n_resp, " responses"),
  showcase = bsicons::bs_icon("3-circle-fill"),
  p(paste0("A: ", b$pct_A, "% · B: ", b$pct_B, "% · C: ", b$pct_C, "%")),
  p(mis_txt),
  theme    = value_box_theme(bg = dom_col, fg = "#ffffff")
)
```

```{r rce_vb_b4}
#| padding: 4px
b <- rce_block[rce_block$block == 4, ]
if (nrow(b) == 0) b <- data.frame(block=4,n_resp=0,freq_A=0,freq_B=0,freq_C=0,pct_A=0,pct_B=0,pct_C=0,mismatches=0)
dom_col <- if (b$pct_A >= b$pct_B & b$pct_A >= b$pct_C) "#004D40" else
           if (b$pct_B >= b$pct_C) "#26A69A" else "#B2DFDB"
mis_txt <- if (b$mismatches > 0) paste0("⚠️ ", b$mismatches, " mismatch(es)") else "✅ 0 mismatches"
value_box(
  title    = "Block 4 · RCE",
  value    = paste0(b$n_resp, " responses"),
  showcase = bsicons::bs_icon("4-circle-fill"),
  p(paste0("A: ", b$pct_A, "% · B: ", b$pct_B, "% · C: ", b$pct_C, "%")),
  p(mis_txt),
  theme    = value_box_theme(bg = dom_col, fg = "#ffffff")
)
```

## Row {height="280px"}

```{r rce_chart_b1}
#| title: "📊 Block 1 · A / B / C Distribution"
rc_colors <- c("#004D40", "#26A69A", "#B2DFDB")
b <- rce_block[rce_block$block == 1, ]
if (nrow(b) == 0) b <- data.frame(freq_A=0, freq_B=0, freq_C=0, n_resp=1)
tot <- max(b$freq_A + b$freq_B + b$freq_C, 1)
plot_ly(
  x    = c("A","B","C"),
  y    = c(b$freq_A, b$freq_B, b$freq_C),
  type = "bar",
  marker      = list(color = rc_colors, line = list(width = 0)),
  text        = paste0(c(b$freq_A, b$freq_B, b$freq_C), "<br>",
                       round(c(b$freq_A, b$freq_B, b$freq_C) / tot * 100, 1), "%"),
  textposition = "outside",
  hovertemplate = "%{x}: %{y} responses (%{text})<extra>Block 1</extra>"
) |>
  pl_layout(showlegend = FALSE,
            yaxis = list(rangemode = "tozero", title = "Responses"),
            xaxis = list(title = "Choice")) |>
  config(displayModeBar = FALSE)
```

```{r rce_chart_b2}
#| title: "📊 Block 2 · A / B / C Distribution"
b <- rce_block[rce_block$block == 2, ]
if (nrow(b) == 0) b <- data.frame(freq_A=0, freq_B=0, freq_C=0, n_resp=1)
tot <- max(b$freq_A + b$freq_B + b$freq_C, 1)
plot_ly(
  x    = c("A","B","C"),
  y    = c(b$freq_A, b$freq_B, b$freq_C),
  type = "bar",
  marker      = list(color = rc_colors, line = list(width = 0)),
  text        = paste0(c(b$freq_A, b$freq_B, b$freq_C), "<br>",
                       round(c(b$freq_A, b$freq_B, b$freq_C) / tot * 100, 1), "%"),
  textposition = "outside",
  hovertemplate = "%{x}: %{y} responses<extra>Block 2</extra>"
) |>
  pl_layout(showlegend = FALSE,
            yaxis = list(rangemode = "tozero", title = "Responses"),
            xaxis = list(title = "Choice")) |>
  config(displayModeBar = FALSE)
```

```{r rce_chart_b3}
#| title: "📊 Block 3 · A / B / C Distribution"
b <- rce_block[rce_block$block == 3, ]
if (nrow(b) == 0) b <- data.frame(freq_A=0, freq_B=0, freq_C=0, n_resp=1)
tot <- max(b$freq_A + b$freq_B + b$freq_C, 1)
plot_ly(
  x    = c("A","B","C"),
  y    = c(b$freq_A, b$freq_B, b$freq_C),
  type = "bar",
  marker      = list(color = rc_colors, line = list(width = 0)),
  text        = paste0(c(b$freq_A, b$freq_B, b$freq_C), "<br>",
                       round(c(b$freq_A, b$freq_B, b$freq_C) / tot * 100, 1), "%"),
  textposition = "outside",
  hovertemplate = "%{x}: %{y} responses<extra>Block 3</extra>"
) |>
  pl_layout(showlegend = FALSE,
            yaxis = list(rangemode = "tozero", title = "Responses"),
            xaxis = list(title = "Choice")) |>
  config(displayModeBar = FALSE)
```

```{r rce_chart_b4}
#| title: "📊 Block 4 · A / B / C Distribution"
b <- rce_block[rce_block$block == 4, ]
if (nrow(b) == 0) b <- data.frame(freq_A=0, freq_B=0, freq_C=0, n_resp=1)
tot <- max(b$freq_A + b$freq_B + b$freq_C, 1)
plot_ly(
  x    = c("A","B","C"),
  y    = c(b$freq_A, b$freq_B, b$freq_C),
  type = "bar",
  marker      = list(color = rc_colors, line = list(width = 0)),
  text        = paste0(c(b$freq_A, b$freq_B, b$freq_C), "<br>",
                       round(c(b$freq_A, b$freq_B, b$freq_C) / tot * 100, 1), "%"),
  textposition = "outside",
  hovertemplate = "%{x}: %{y} responses<extra>Block 4</extra>"
) |>
  pl_layout(showlegend = FALSE,
            yaxis = list(rangemode = "tozero", title = "Responses"),
            xaxis = list(title = "Choice")) |>
  config(displayModeBar = FALSE)
```

## Row {height="320px"}

```{r rce_enum_heatmap}
#| title: "🔥 Enumerator × Block Heatmap (% dominant choice)"
if (nrow(rce_enum) > 0) {
  heat_df <- rce_enum %>%
    mutate(
      label   = paste0(enumerator, "\n(", supervisor, ")"),
      flag_lbl = if_else(flag_uniform, "🔴", ""),
      dom_pct  = max_pct
    )

  plot_ly(heat_df,
    x    = ~factor(block, labels = paste("Block", 1:4)),
    y    = ~label,
    z    = ~dom_pct,
    type = "heatmap",
    colorscale = list(
      c(0,   "#E0F2F1"),
      c(0.5, "#26A69A"),
      c(0.8, "#004D40"),
      c(1,   "#C62828")
    ),
    zmin = 33, zmax = 100,
    text = ~paste0(enumerator, " | Block ", block,
                   "<br>Dominant: ", dom_pct, "%",
                   "<br>A:", pct_A, "% B:", pct_B, "% C:", pct_C, "%",
                   "<br>Mismatch: ", mismatch,
                   if_else(flag_uniform, "<br>🔴 FLAGGED", "")),
    hoverinfo = "text"
  ) |>
    layout(
      font        = list(family = "Segoe UI, Arial", size = 10, color = "#595959"),
      paper_bgcolor = "rgba(0,0,0,0)",
      plot_bgcolor  = "rgba(0,0,0,0)",
      xaxis  = list(title = "", side = "top"),
      yaxis  = list(title = "", tickfont = list(size = 9)),
      margin = list(l = 140, r = 60, t = 40, b = 20),
      coloraxis = list(colorbar = list(
        title = "Dominant %", ticksuffix = "%", len = 0.8
      ))
    ) |>
    config(displayModeBar = FALSE)
} else {
  HTML('<p style="color:#888;padding:20px">No RCE data available.</p>')
}
```

## Row

```{r rce_mismatch_chart}
#| title: "⚠️ Total Mismatches per Enumerator (all blocks)"
if (nrow(rce_enum) > 0) {
  mis_by_enum <- rce_enum |>
    group_by(enumerator, supervisor) |>
    summarise(mis = sum(mismatch, na.rm = TRUE), .groups = "drop") |>
    arrange(mis) |>
    mutate(
      label     = paste0(enumerator, " (", supervisor, ")"),
      bar_color = case_when(
        mis > 2 ~ "#C62828",
        mis > 0 ~ "#FF8F00",
        TRUE    ~ "#00695C"
      )
    )

  plot_ly(mis_by_enum,
    y    = ~label, x = ~mis,
    type = "bar", orientation = "h",
    marker        = list(color = ~bar_color, line = list(width = 0)),
    text          = ~if_else(mis > 0, as.character(mis), ""),
    textposition  = "outside",textfont = list(size = 14),
    hovertemplate = "%{y}: %{x} mismatch(es)<extra></extra>") |>
    pl_layout(
      showlegend = FALSE,
      yaxis = list(categoryorder = "array",
                   categoryarray = mis_by_enum$label,
                   title = "", tickfont = list(size = 9)),
      xaxis = list(rangemode = "tozero", dtick = 1, title = "Mismatches"),
      margin = list(l = 160, r = 50, t = 30, b = 40)
    ) |>
    config(displayModeBar = FALSE)
} else {
  HTML('<p style="color:#888;padding:20px">No RCE data available.</p>')
}
```

## Row {height="auto"}

```{r rce_enum_table}
#| title: "👥 Enumerator Detail by Block"
#| padding: 0px
if (nrow(rce_enum) > 0) {
  # Build inline mini-bar HTML for a percentage value and colour
  mini_bar <- function(pct, col) {
    w <- round(pct * 0.65)
    sprintf('<div style="display:inline-block;width:%dpx;height:7px;background:%s;
             border-radius:2px;vertical-align:middle;margin-left:3px"></div>', w, col)
  }

  tbl_df <- rce_enum %>%
    arrange(block, desc(flag_uniform), desc(mismatch), enumerator) %>%
    mutate(
      Block      = paste0("Block ", block),
      Enumerator = enumerator,
      Supervisor = supervisor,
      Resp       = n_resp,
      `A (n/%)`  = paste0(freq_A, " / ", pct_A, "%",
                          mini_bar(pct_A, "#004D40")),
      `B (n/%)`  = paste0(freq_B, " / ", pct_B, "%",
                          mini_bar(pct_B, "#26A69A")),
      `C (n/%)`  = paste0(freq_C, " / ", pct_C, "%",
                          mini_bar(pct_C, "#B2DFDB")),
      Mismatch   = if_else(mismatch > 0,
                           paste0('<span style="background:#FF8F00;color:#fff;padding:1px 6px;
                                   border-radius:10px;font-size:11px">', mismatch, '</span>'),
                           "0"),
      Flag       = if_else(flag_uniform,
                           '<span style="color:#C62828;font-weight:700;font-size:13px">🔴 Flagged</span>',
                           '<span style="color:#00695C">✅</span>')
    ) %>%
    select(Block, Enumerator, Supervisor, Resp,
           `A (n/%)`, `B (n/%)`, `C (n/%)`, Mismatch, Flag)

  # Render using knitr::kable with bootstrap styling
  knitr::kable(tbl_df, format = "html", escape = FALSE,
               table.attr = 'class="table table-sm table-hover" style="font-size:12px"') |>
    kableExtra::kable_styling(bootstrap_options = c("striped","hover","condensed"),
                              full_width = TRUE) |>
    kableExtra::row_spec(which(rce_enum$flag_uniform), background = "#FFF3E0")
} else {
  HTML('<p style="color:#888;padding:20px">No RCE data available.</p>')
}
```